---
title: "The Post Mortom Airtime effect"
output: html_document
---

I was busy on a little side project on Radio Playlists when the news broke about the death of Dolores O’Riordan, front singer of The Cranberries. And sure enough, a few hours later I could see The Cranberries starting to pop up in the playlists.  
Their second album *No Need to Argue* was one of my favourite CD's as a teenager, and guided me through some rough times. So I wondered: how many times would they be played? And it would it all be 'Zombie', or would some of their other gems get air time as well?

## Scraping the playlist
There is a website that contains playlists for quite a few Belgian radio stations (unfortunately only the Flemish ones). By using this site rather then the radio's own sites, I could scrape different broadcasting companies with one script. I did do some random checks to make sure that the playlists were matching though.  
  
First loading the packages needed and checking whether I am allowed to scrape this site via the `robotstxt` package.

```{r message=FALSE, warning=FALSE}
library(rvest)
library(xml2)
library(tidyverse)

robotstxt::paths_allowed("https://www.relisten.be/playlists/")
```


I wrote a `read_playlist` funcion to scrape the data into a dataframe with 5 columns: station, date, timestamp, artist and title. I immediately made a second version for those times I would need to iterate this function, called `read_playlist_and_sleep` which just adds 5 seconds in between every iteration.
```{r}

#function to read a playlist, returnin a dataframe with timestamp, artist and title of song
read_playlist <- function(radio, date){

  #assemble link
  link <- paste0("https://www.relisten.be/playlists/", radio, "/", date, ".html")

  #playlist info
  html_playlist <- read_html(link) %>%
    html_nodes(css = "#playlist")

  #get time info
  time <- html_playlist %>%
    html_nodes(css = ".media-body > h4 > .pull-right") %>%
    html_text()
  
  #get title info
  title <- html_playlist %>%
    html_nodes(css = ".media-body > h4 > span") %>%
    html_text()
  
  #get artist info
  artist <- html_playlist %>%
    html_nodes(css = ".media-body > p > a > span") %>%
    html_text()
  
    #check for empty pages and return NA if that's the case - otherwise purrr::map will fail later on
  if (length(artist) == 0) {return(NULL)}

  #assembling the dataframe
  playlist <- data.frame(radio, date, time, title, artist, stringsAsFactors = FALSE)
  playlist$date <- lubridate::dmy(playlist$date)
  playlist
}


#adding system sleep to function
read_playlist_and_sleep <- function(radio, date) {
  Sys.sleep(5)
  read_playlist(radio, date)
}